---
title: "Homework Two"
output: html_document
---

# Homework Two: Due Sept. 13 at 5 pm.

First, download your homework. In your RStudio, enter:

```{r}
download.file("https://raw.githubusercontent.com/BiologicalDataAnalysis2019/2019/master/homeworks/HomeworkTwo.Rmd", destfile = "/cloud/project/homeworks/HomeworkTwo.Rmd")
download.file("https://raw.githubusercontent.com/BiologicalDataAnalysis2019/2019/master/homeworks/surveys.csv", destfile = "/cloud/project/homeworks/surveys.csv")
```

In your RStudio interface, you will note that there is now a "Homeworks" directory. In it, you will find "HomeworkTwo.Rmd". In your RStudio instance, open it.

Each question will direct you to perform a task. Each question that expects code as an answer will have a space for you to enter the code. 

You are welcome, and even encouraged, to work with a partner. I do ask, though, that every member submits their own homework. To submit your homework, simply save it. I will see it.


## Question One - 1 point.

Load in the `surveys.csv` data file that is located in your homework folder, and save it to a variable called `surveys`. Use the read_csv function in the `tidyverse` package to do this.

```{r}
#Enter your answer for Question 1 here

```

## Question Two - 1 point

Have a look at the copy of `surveys.csv`. You will notice that there are some unusual NA values. Look at the help page for `read_csv`. Can you find a way to read these unusual values as NAs? Try it out.
```{r}
#Enter your answer for Question 2 here

```

## Question Three - 1 point

Remove the NA values from the `hindfoot_length` column using a pipe and a filter.
```{r}
#Enter your answer for Question 3 here

```

## Question Four - 2 points

Verify that the NA values were removed. Don't do this by looking at the column - use code.
```{r}
#Enter your answer for Question 4 here

```

## Question Five - 1 point

Explain the logic of your answer to Question Four.


## Question Six - 1 point

Imagine you are testing the hypothesis that mammal body sizes will be smaller under climate change to increase surface to body size ratio. First, what columns in the dataframe will you use to address this question? 


## Question Seven - 2 points

Let's try some analysis: Use a `filter`, a `group_by`, and a `summarize` to decide if you think mammal body sizes are decreasing under climate change.

```{r eval=FALSE}


```

## Question Eight - 1 points

Based on the outputs of question 7, does it look like mammal body sizes are decreasing?