---
title: "HomeworkOne.Rmd"
output: html_document
---

# Homework One: Due Sept. 6 at 5 pm.

First, download your homework. In your RStudio, enter:

```{r}
dir.create("/cloud/project/homeworks")  
download.file("https://raw.githubusercontent.com/BiologicalDataAnalysis2019/2019/master/homeworks/HomeworkOne.Rmd", destfile = "/cloud/project/homeworks/HomeworkOne.Rmd")
```

Your homework will now be located in a directory called `homeworks`.


In your RStudio interface, you will note that there is now a "Homeworks" directory. In it, you will find "HomeworkOne.Rmd". In your RStudio instance, open it.

Each question will direct you to perform a task. Each question that expects code as an answer will have a space for you to enter the code. 

You are welcome, and even encouraged, to work with a partner. I do ask, though, that every member submits their own homework. To submit your homework, simply save it. I will see it.


## Question One - 1 point.

Load in the surveys.csv data file, and save it to a variable called "surveys".

```{r}
#Enter your answer for Question 1 here

```

## Question Two - 1 point

What is the mean hindfoot length? Show your work below:
```{r}
#Enter your answer for Question 2 here

```

## Question Three - 1 point

Save the `hindfoot_length` column to its own variable, called `hindfoot_vector`.
```{r}
#Enter your answer for Question 3 here

```

## Question Four - 2 points

Calculate the mean of the `hindfoot_vector`. Does it work? 
```{r}
#Enter your answer for Question 4 here

```
In your own words, why did it not work? 


## Question Five - 1 point

Test your idea about why it didn't work by writing some code that will fix the problem.
```{r}
#Enter your answer for Question 5 here

```

## Question Six - 2 points

We included an example in class that was a little confusing. Can you explain, in your own words, why the code gives the result it does?

```{r}
animals <- c("mouse", "rat", "dog", "cat")
animals %in% c("rat", "cat", "dog", "duck", "goat")

```
Enter your explanation here:

## Question Seven - 2 points

I have written some code to calculate the mean of the hindfoot. But it's not working! Correct my code. 

```{r eval=FALSE}
surveys <- read.csv("/cloud/project/data/surveys.csv")
hindfoot_vector <- surveys[7]
hindfoot_mean <- (sum(hindfoot_vector)/length(hindfoot_vector))
```
