---
title: "Homework Five"
output: html_document
---

# Homework Two: Due Oct. 9 at 5 pm.

First, download your homework. In your RStudio, fill in the below command:

```{r, eval = FALSE}
download.file(url = "https://raw.githubusercontent.com/BiologicalDataAnalysis2019/2020/master/vignettes/HomeworkFive.Rmd", destfile = "/cloud/project/homeworks/HW5.Rmd")

```

# Question One (1 pts):
We're going to work with the NOAA data again. This time, I'm going to have you go to [the raw data](https://www.ncei.noaa.gov/data/global-historical-climatology-network-daily/access/) and download the data for USW00003145. Upload it to your data directory.  


# Question Two (1 pts)

Read in the data

```{r}
raw_data_NOAA <- read_csv("../data/USW00003145.csv")

```

# Question 3 (3 pts)

Merge this dataframe to the NOAA dataframe we save from Monday's class. 

Hint: You may need to specify "by" arguments. Possibly multiple.
```{r}
temp_data %>%
     rename(STATION = id, DATE = date, TMAX = tmax, TMIN = tmin)
NOAA_combined <- merge(temp_data, raw_data_NOAA)
```

#AMW: You'll need to use the "by" arguments
this keeps crashing R - did not work
#TBC: I have not been able to get the by argument to work

# Question 4 (2 pts)

Drop any rows for which the "TMAX_ATTRIUBTES" or "TMIN_ATTRIBUTES" contain an X
```{r}
NOAA_combined <- NOAA_combined %>%
  filter(TMAX_ATTRIBUTES != ",,X" & TMIN_ATTRIBUTES !=",,X")
```

# Question 5 (1 pts)

How many rows did we lose in this quality control? 

```{r}
4956
```

# Question 6 (2 points)

Merge your filtered data to the surveys_complete dataset and try replotting it. Did this make a difference to our conclusions from Wednesday?

```{r}
NOAA_combined_complete <-merge(NOAA_combined, new_surveys)
```


## MS Students:

For last week, I had you populate function templates in your personal directory. I'm going to update this homework Monday when I've had a chance to look at them.

