---
title: "Homework Three"
output: html_document
---

# Homework Four: Due Oct. 4 at 5 pm.

First, download your homework. In your RStudio, fill in the below command:

```{r, eval = FALSE}
download.file()

```

# Question One. 2 pts:

Take a look at [this](https://github.com/ropensci/treedata.table/) package. Reading the documentation, what is the primary goal of this package? 

```
#Answer Here
```

# Question Two. 1 pts

Where in this package is the actual code stored? How do you know?

```
# Answer here

```

# Question 3. 3 pts

When you look into the code, are you able to understand any of it? What is one thing the authors could do to make the code more understandable?

```
# Answer here
```

# Question 4. 2 pts

What are the other directories in the package? What do they contain?

```
Answer here

```

# Question 4. 2 pts
Do you trust this package? Why or why not? What about this package makes it trustworthy or untrustworthy?

```{r}


```

# Question 5. 2 pts.

Have a look at [these](https://libguides.bc.edu/dataplan/best_practices) data storage best practices from Boston College. Are we doing a good job so far in class? Why or why not? What could be improved? 

## Grad Students

Goal setting time! Ideally, each function you write should be in a .R file in your R directory. In your personal project directory (i.e., the one we made in class with your last name Wednesday), please make three .R files. Title each with the name of the function you will write.
Ideally, these functions will do something that you need done for your dissertation. 
Begin the documentation for each by writing the first documentation line - the line that is a one-sentence summary of what the function does. I'm going to take a look through these and make sure we're covering the right material for you to get your work done.