---
title: "Homework Two"
output: html_document
---

# Homework One: Due Sept. 11 at 5 pm.

First, download your homework. In your RStudio, enter:

```{r}
download.file(url = "https://raw.githubusercontent.com/BiologicalDataAnalysis2019/2020/master/vignettes/HomeworkTwo.Rmd", destfile = "/cloud/project/homeworks/HW2.Rmd")
```

Your homework will now be located in a directory called `homeworks`.


In your RStudio interface, you will note that there is now a "Homeworks" directory. In it, you will find "HomeworkTwo.Rmd". In your RStudio instance, open it.

Each question will direct you to perform a task. Each question that expects code as an answer will have a space for you to enter the code. 

You are welcome, and even encouraged, to work with a partner. I do ask, though, that every member submits their own homework. To submit your homework, simply save it. I will see it.


## Question One - 1 point.

Load in the surveys.csv data file, and save it to a variable called "surveys".

```{r}
#Enter your answer for Question 1 here

```

## Question Two - 1 point

What is the mean hindfoot length? Show your work below:
```{r}
#Enter your answer for Question 2 here

```

## Question Three - 1 point

Save the `hindfoot_length` column to its own variable, called `hindfoot_vector`.
```{r}
#Enter your answer for Question 3 here

```

## Question Four - 2 points

Calculate the mean of the `hindfoot_vector`. Does it work? 
```{r}
#Enter your answer for Question 4 here

```
In your own words, why did it not work? 


## Question Five - 1 point

Test your idea about why it didn't work by writing some code that will fix the problem.
```{r}
#Enter your answer for Question 5 here

```

## Question Six - 2 points

We included an example in class that was a little confusing. Can you explain, in your own words, why the code gives the result it does?

```{r}
animals <- c("mouse", "rat", "dog", "cat")
animals %in% c("rat", "cat", "dog", "duck", "goat")

```
Enter your explanation here:

## Question Seven - 2 points

I have written some code to calculate the mean of the hindfoot. But it's not working! Correct my code. 

```{r eval=FALSE}
surveys <- read.csv("/cloud/project/data/surveys.csv")
hindfoot_vector <- surveys[7]
hindfoot_mean <- (sum(hindfoot_vector)/length(hindfoot_vector))
```


## For the Graduate Students

Each of you sent in a spreadsheet to me. They looked good. They'll work. But I'd like each of you to think about the data in those spreadsheets.

1. If your data are saved in Excel format, under the `File` menu in Excel, Save As -> csv. To keep it simple for now, if you have multiple worksheets in your Excel file, just pick a single one for now. Upload it to your RStudio Cloud and save in the data folder.

2. Read it in with `read.csv`. Are the types of the columns appropriate? 


3. Do your NA values read in appropriately? If you drop NAs from your dataframe, does the resultant dataframe seem to have the correct rows or columns dropped?

4. Dates. Are they formatted consistently? If not, fix with `lubridate`. 

5. What are you looking to do with this data? Make sure you actually want to do this task - you might see it again ;p